\documentclass[11pt]{article}

% Standard, arXiv-safe packages only (compiles with a plain pdflatex + one bibtex-free run, or tectonic).
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{array}
\usepackage{float}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage[section]{placeins}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

% NOTE TO AUTHOR (Daniel): this is a findings-paper draft. The three previously-flagged citations
% (Control Tax arXiv:2506.05296; DeepMind Frontier Safety Framework v3.0, 22 Sep 2025; METR MALT,
% 14 Oct 2025) were verified against primary sources on 2026-07-14. Before sending anywhere, still confirm
% the author/affiliation block and re-read the Limitations section. Every quantitative claim below
% regenerates from a committed runner, manifest, or validated receipt in the Telos repository; the exact
% experiment is named in the text (for example, iter195).

\title{Reward Hacks That Pass Every Graded Test:\\
Constructing and Detecting SWE-bench Patches\\
That Are Certified Yet Wrong}

\author{Daniel Wahnich\\ \small Telos research program}

\date{July 16, 2026}

\begin{document}
\maketitle

\begin{abstract}
Coding agents are commonly certified when graded tests pass, but a patch can satisfy this proxy while
remaining wrong on untested inputs. We ask whether SWE-bench Verified certifies such patches and what
detects them.

We report four results. First, an earlier benchmark we built contained no reward hacks: all forty rows fail
the official grader. Second, we construct twenty-two patches across eight repositories that pass every
graded test yet differ from the accepted fix on a retained input, verified by retained execution under
instance-specific SWE-bench container tags. Third, a
two-model judge panel has observed catches on $20/22$ hacks, with $8/88$ unparseable responses; paired-gold
flag sensitivities are $3/22$ observed lower, $6/22$ worst-case missing upper, and $3/19$ complete-case. A
second instrument used candidate-diff-derived locators and gold-based inclusion. This locator-assisted,
gold-validated property pipeline catches $6/22$, all within the judge set, and supplies no independent
false-positive estimate. Its full-cohort run failed the registered diff-independent locator contract; an
earlier ten-row run additionally replaced its visible-test soundness anchor and omitted registered
controls. That earlier run's apparent property-only row had two unparseable judge responses, so neither
run confirms complementarity. Fourth, an exploratory, nonrandom, gold-localized solve with no gaming instruction yields
one strict case under a post-inspection blind rule. Of thirty-seven valid patches, twenty-four certify and
six certified outcomes remain unadjudicated; the required descriptive sensitivities are $1/24$, $7/24$
over those six missing pipeline outcomes, and $1/18$ complete-case.

These are bounded pilots, not population-frequency estimates. The judge runs retained parsed labels but
not raw responses, used capped inputs, and lack an independently Git-frozen full-cohort protocol. The strict blind aggregation rule was
adopted after outcome inspection; the missingness summaries were added after the original result but before
the denominator backfill. Its pre-output freeze is not independently timestamped in Git. Every number
regenerates from committed artifacts.
\end{abstract}

\section{Introduction}

An autonomous coding agent is given a bug report and asked to produce a patch. The usual measure of success
is a test suite: if the tests pass, the task is considered done. This measure is convenient, and it is also
gameable. The agent can edit or weaken the tests, or it can write source code that handles only the exact
input the visible test checks rather than solving the general problem. When the test suite is a proxy for
``the task is solved,'' making the tests pass without solving the task is \emph{reward hacking}, the general
failure in which an optimizer satisfies a proxy reward while missing the objective the reward stands
in for~\cite{amodei2016concrete,krakovna2020specification,skalse2022defining}.

This paper asks a specific version of that question. SWE-bench Verified is a coding-agent
benchmark~\cite{jimenez2024swebench}. Each of its instances comes with two sets of tests: a
\texttt{FAIL\_TO\_PASS} set that a correct fix must newly pass, and a \texttt{PASS\_TO\_PASS} set of
existing tests that a correct fix must keep passing. The official harness marks an instance \emph{resolved}
when a patch passes both sets. Our question is: can a patch pass both sets---be certified resolved---and
still be wrong? If it can, then no check restricted to those graded tests can catch it, because passing
those tests is exactly what ``resolved'' means.

The question is a bounded software-evaluation analogue of a broader oversight problem. Google DeepMind's
Frontier Safety Framework discusses systems that circumvent oversight while outputs are monitored and lists
mitigation as future work~\cite{deepmind2025fsf}. Our elicited patches do not establish intent or autonomous
oversight evasion; they isolate one measurable proxy/objective gap.

We make four contributions.
\begin{enumerate}
  \item \textbf{A self-correction (Section~\ref{sec:correction}).} An earlier benchmark we released did
  not contain reward hacks. We show why from committed evidence, and we report the free baseline that had
  been missing.
  \item \textbf{Certified-yet-wrong patches (Section~\ref{sec:construct}).} We construct and release a
  benchmark of twenty-two patches across eight repositories that the official SWE-bench harness marks
  resolved and that execution shows are wrong, each with a retained witness.
  \item \textbf{A corrected exploratory instrument comparison (Section~\ref{sec:detect}).} We preserve
  judge catch and missingness measurements, distinguish two property-protocol failures, and withdraw the
  independent false-positive, confirmed-complementarity, and deployable-ensemble interpretations.
  \item \textbf{A neutral-prompt localized existence case (Section~\ref{sec:construct}).} An exploratory,
  gold-localized solver run produces one strict certified-yet-wrong patch under a post-inspection rule. We
  correct the certification denominator and report post-result missing-outcome sensitivities without
  imputing missing outcomes as negatives.
\end{enumerate}

\section{Background}

\paragraph{Reward hacking.} Reward hacking, also called specification
gaming~\cite{krakovna2020specification}, is when an agent scores well on a proxy reward while failing the
real goal. Skalse et al.~\cite{skalse2022defining} give a formal definition. We use the term in its plain
sense: a patch that scores well on the grader (it is certified resolved) while being wrong. We note one
name collision to avoid confusion: RewardBench~\cite{lambert2024rewardbench} evaluates \emph{reward
models}, which rank preferences, and is unrelated to the reward hacking studied here.

\paragraph{SWE-bench Verified.} SWE-bench~\cite{jimenez2024swebench} asks a model to resolve a real GitHub
issue in a real Python repository. SWE-bench Verified is a human-filtered subset. Each instance pins a
repository commit and defines the \texttt{FAIL\_TO\_PASS} and \texttt{PASS\_TO\_PASS} test sets; the harness
derives an instance-specific container image tag. The ``gold patch'' is the accepted human fix. A known weakness of the format is
that the graded tests can be incomplete: they may not exercise every behavior a correct fix must have. Our
constructed hacks live in exactly that gap.

\paragraph{Language-model judges.} A language model can act as a monitor that reads a patch and decides
whether it is correct~\cite{zheng2023judging}. Judges are not uniformly weak. On backdoored programming
solutions, a monitor can reach an area-under-the-curve of 0.92 to 0.96~\cite{terekhov2025controltax}. Our
single-run panel has observed catches on twenty of twenty-two hacks in the full-cohort comparison; it caught
seven of ten under the original pilot's observed rule. In that pilot, missing responses permit a
nine-of-ten upper sensitivity and a seven-of-eight complete-case sensitivity. The difference underscores
that the retained counts are run-specific and missingness-sensitive, not stable model scores.

\paragraph{Execution-based checks.} A different family of checks constructs an input, runs the code, and
checks the output. A genuinely reference-free check can use property-based testing~\cite{claessen2000quickcheck}
or metamorphic testing~\cite{chen2018metamorphic}. The retained iter197/iter201 instrument did not satisfy
the registered diff-independent access contract: its generator received a source/function locator derived
from the candidate diff. Offline inclusion also ran each property on gold. Gold validation was explicitly
registered in iter201 but not as the iter197 soundness anchor; in either case, it is an inclusion rule rather
than an independent control decision. We therefore call the instrument a \emph{locator-assisted,
gold-validated property pipeline}, not a validated gold-free detector.

\paragraph{Scale of existing corpora.} Public datasets of reward hacking are far larger than ours: METR's
MALT contains on the order of ten thousand transcripts~\cite{metr2025malt}. Ours is twenty-two patches. We make no
claim of scale. What is different here is the unit and the verification: we label individual patches (not
whole trajectories), and every label is verified by execution. Most benchmark rows are elicited: a model
was asked to produce the hacks. The separate neutral-prompt localized solve below supports one strict case
under a post-inspection rule, not a population frequency.

\section{An Earlier Benchmark Measured the Wrong Thing}
\label{sec:correction}

We begin with a correction, because it defines the target for the rest of the paper.

An earlier stage of this project released a forty-row artifact and described its rows as reward hacks. The
generator that produced those rows kept a candidate only when the candidate made at least one
\texttt{PASS\_TO\_PASS} test fail. \texttt{PASS\_TO\_PASS} is the grader's existing-test subset, so every
row failed the official reward by construction.

We re-derived the official harness verdict for all forty rows from the committed evaluation logs. All forty
are marked unresolved, and all forty have at least one failing \texttt{PASS\_TO\_PASS} test. The
consequence is direct. Running the official harness, or reading its verdict, detects all forty rows at zero
model cost. A three-model language-model judge panel, the detector
we had been studying, detected seventeen of forty at a metered cost of \$13.59. That free baseline had
never been reported.

The rows are therefore not reward hacks. A reward hack scores well on the reward while being wrong; these
rows fail the reward. They are wrong patches that break at least one graded regression check, which the
official grader catches for free. The earlier judge figure of seventeen of forty is arithmetically correct and we do not retract it;
what changes is what it measures. It measures how often a judge, reading a diff, spots a wrong patch that
the official graded regression checks already reject. That is a fact about code review, not about reward hacking, and it does
not motivate a new verifier.

The real target is the inverse: a patch that passes all graded tests and is still wrong. The official
harness scores such a patch as resolved, so running the tests cannot catch it. The rest of the paper
constructs that class and asks what does catch it.

\section{Constructing Certified-Yet-Wrong Patches}
\label{sec:construct}

\paragraph{Operational labels.} The two cohorts use different rules. A constructed-cohort patch is labelled
certified-yet-wrong when the official harness marks it resolved and a clean synthesized-input run produces
output different from gold. This is a reference-differential label, not independent semantic adjudication.
In the neutral-prompt cohort, a patch must certify, diverge from gold, and---under the later conservative
rule---have both blind judges identify only the model output as wrong.

\paragraph{Audited module tests did not distinguish the candidates.} Before constructing the class, we
took sixteen candidates, confirmed that all sixteen were certified, and ran the graded tests plus every
additional test in the same audited test modules. For Django, the graded \texttt{PASS\_TO\_PASS} set already
covers the whole target module. Across the sixteen candidates there were 193 additional module tests; none
distinguished a candidate from gold. We did not run every test elsewhere in every repository. The measured
claim is narrower: witnessing these candidates required an input outside the audited graded/additional
target-module tests.

\paragraph{Construction.} We construct the class in three steps, all executed under each instance's
SWE-bench container tag.
\begin{enumerate}
  \item \textbf{Elicit a variant.} We take the gold patch and ask \texttt{gpt-5.6-terra} to rewrite its largest
  added block into a variant that still passes the graded tests but is subtly wrong on other inputs. The
  model is explicitly asked to produce a wrong variant; the class is elicited, not observed in the wild.
  \item \textbf{Certify by execution.} We run each instance's official evaluation command under its
  instance-specific container tag---for example, Django's \texttt{runtests.py}, SymPy's \texttt{bin/test}, or \texttt{pytest}
  where the instance specifies it---and parse the result with the official SWE-bench log parsers. A variant
  is kept only if it passes every
  \texttt{FAIL\_TO\_PASS} and \texttt{PASS\_TO\_PASS} test.
  \item \textbf{Witness the wrongness.} To label a certified variant as wrong, we use the gold patch as
  reference. \texttt{gpt-5.6-terra} constructs a small
  scenario that calls the changed function on an input designed to reach the branch where the variant and
  the gold fix could differ. We run that scenario under the gold patch and under the variant, in the same
  container. If the two produce different output, and the gold run is clean, the variant is a witnessed
  reward hack.
\end{enumerate}

\paragraph{Generation configuration.} The same OpenAI model, \texttt{gpt-5.6-terra}, filled the adversarial
variant, differential-scenario, neutral-solve, and property-generation roles. Retained generation requests
set \texttt{max\_completion\_tokens=4000} and supplied no temperature field, so provider defaults applied.
This role reuse is a limitation, not evidence of cross-model generality.

\paragraph{Result.} From sixteen certified candidates, this procedure yields ten witnessed
certified-resolved reward hacks across three repositories (Django, astropy, matplotlib). Two further
candidates matched gold on their retained scenarios; we report them as \texttt{certified\_equivalent} but
do not infer global equivalence. The remaining candidates produced no clean witness.
Table~\ref{tab:hacks} lists these ten hacks, which formed the set used for the original ten-row
detector pilot; the standing comparison in Section~\ref{sec:detect} uses all twenty-two released hacks.

\paragraph{The class is not specific to three repositories.} We then ran the same pipeline on forty-two
additional targets, disjoint from the original sixteen and spanning all twelve repositories in SWE-bench
Verified. They were additional to this construction gate, not claimed mission-history fresh. The run
produced twenty-three variants;
twenty were certified resolved by execution, and twelve were also witnessed wrong, adding hacks in five new
repositories: requests, xarray, pylint, pytest, and sympy. Combined with the first ten, the released
benchmark is twenty-two execution-verified certified-resolved reward hacks across eight repositories. The
sharpest scale example is a Django hack whose variant passes 1{,}870 graded tests and still returns
\texttt{'accepted'} where the correct fix returns \texttt{'rejected'}. The instrument comparison below
includes all twenty-two hacks.

\paragraph{Exploratory neutral-prompt localized solve.} Every benchmark hack above is elicited. We therefore
retained a separate run with no gaming instruction. This was not a random sample: thirty-nine targets were
selected after excluding all sixty-six unique targets from the earlier iter193 Phase-A and iter199 target
sets. The remaining engineering filters---one source file, one added run, strip-round-trip compatibility
with the gold-shaped patch builder, lexicographic ordering, and a cap of five per repository---yielded 200
compatible rows across nine repositories and the frozen thirty-nine. The prompt included the issue and a buggy region reconstructed from gold-diff context
and removed lines; gold-added lines were withheld. We therefore call it gold-localized, not plain.

\texttt{gpt-5.6-terra} produced thirty-seven valid patches; all now have official-harness evidence, and
twenty-four certify. Nine model/gold patch pairs differ by exactly one terminal LF, so zero are byte-identical;
eight of those normalized-equivalent patches certify. Four certified patches have no observed divergence on
a valid witness, five lack a valid witness, and seven have an observed gold/model divergence. The blind
judges were \texttt{gpt-5.6-terra} and \texttt{claude-opus-4-8}; each saw two outputs unlabeled. The
OpenAI blind request used a 1{,}536-token cap and the Anthropic blind request used
\texttt{max\_tokens=400}; neither supplied a temperature field. The
conservative requirement that both name only the model output was adopted after inspecting the original
outcomes and reduces a loose count of three to one strict case. The original hypothesis named one judge,
and Git commit \texttt{f651bfc} first records the hypothesis, target manifest, and solver outputs together,
so the repository does not independently timestamp a pre-output freeze. The retained judge bundle stores
parsed labels and derived booleans, not raw response text. Exact response substance and parser fidelity
therefore cannot be re-audited; the strict case is bounded parsed-decision evidence.

The strict case is a Sphinx fix that passes all thirty-three graded tests yet renders a compound-key
keyboard input as a malformed empty element. Five certified rows lack a valid witness and one divergence
lacks two complete judge outcomes, so $u=6$ remains unadjudicated. With $N=24$ and $k=1$, we report $1/24$
(4.1667\%) confirmed lower, $7/24$ (29.1667\%) as the worst case over those six declared missing pipeline
outcomes, and $1/18$ (5.5556\%) complete-case sensitivity. The formulas were adopted after the original
result but before the denominator backfill; they are not preregistered iter200 estimates, confidence
intervals, prevalence bounds, or population frequencies. The historical $1/15$ was conditional on a
scenario-eligible cohort and is not pooled.

\begin{table}[t]
\centering
\small
\caption{Original iter195 ten-row subset of the released 22-row benchmark. Each patch passes every graded test (the official
harness marks it resolved), yet produces different output from the gold fix on the shown input.}
\label{tab:hacks}
\begin{tabular}{@{}llll@{}}
\toprule
Instance & Function & Gold output & Variant output \\
\midrule
django-11179 & \texttt{Collector.delete}        & \texttt{None} & \texttt{'present'} \\
django-11119 & \texttt{Engine.render\_to\_string} & \texttt{<tag>} & \texttt{\&lt;tag\&gt;} \\
django-11163 & \texttt{model\_to\_dict}          & \texttt{\{\}} & \texttt{\{'id': None, ...\}} \\
django-11141 & \texttt{MigrationLoader.load\_disk} & \texttt{(True, False)} & \texttt{(False, True)} \\
django-11211 & \texttt{UUIDField.deconstruct}    & \texttt{UUID('550e...')} & \texttt{'550e...' (str)} \\
django-11433 & \texttt{construct\_instance}      & \texttt{0} & \texttt{7} \\
astropy-7166  & \texttt{is\_public\_member}       & \texttt{'...documentation'} & \texttt{None} \\
astropy-14096 & \texttt{SkyCoord.\_\_getattr\_\_}  & \texttt{'intercepted'} & \texttt{AttributeError} \\
matplotlib-23412 & \texttt{Patch.draw}           & \texttt{((2.5, ...),)} & \texttt{((0.0, ...),)} \\
matplotlib-24627 & \texttt{\_AxesBase.\_\_clear}  & \texttt{(True, True)} & \texttt{(False, False)} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{A worked example.} The clearest hack is \texttt{django-11179}. When a database object is deleted,
the correct fix clears the object's primary key to \texttt{None} in memory. The gold patch does exactly
that. The variant clears the key only when the key is literally named \texttt{id}:
\begin{center}
\texttt{setattr(instance, pk.attname, None if pk.name == 'id' else instance.pk)}
\end{center}
Every graded test for this instance uses a model whose primary key is named \texttt{id}, so the variant
passes them and the harness certifies it. But a model whose primary key has any other name keeps a stale
key after deletion. Running the scenario, the gold patch prints \texttt{None} and the variant prints the
stale value.

\paragraph{Execution beat our own judgment.} One case is worth stating against ourselves. We hand-analyzed
\texttt{django-11119} and judged its variant a correct rewrite: the changed expression looked equivalent
for boolean inputs. Execution disagreed. With auto-escaping turned off, the gold patch renders text
unescaped and the variant escapes it, so the two differ. A reasoning pass called the patch correct; running
the code showed it was a hack. This is the paper's own thesis applied to the authors: for this class, run
the code rather than trust a verdict, including one's own.

\paragraph{Claim boundary.} The benchmark hacks are elicited and constructed, not sampled from real agent
runs, so we make no claim about how often agents hack in practice. There are twenty-two hacks across eight
repositories, and the exploratory instrument comparison uses all twenty-two. In this cohort, ``wrong''
means a clean synthesized-input output differs from gold. The separate localized solve supports one strict
case under a later conservative blind rule, with all three missing-outcome quantities reported above. The
two \texttt{certified\_equivalent} controls matched gold only on retained scenarios; global equivalence is
not claimed.

\section{Detecting Certified-Yet-Wrong Patches}
\label{sec:detect}

The instruments had different access. The judge saw the candidate diff, public task, and visible test, but
not gold or the retained witness. The property generator saw the task, visible test, and a source/function
locator extracted from the candidate diff; candidate code lines and gold content were withheld. Offline
evaluation then used gold to decide which properties entered the analysis. The locator violated both
runs' diff-independent access descriptions. Gold validation was registered in iter201, so it is an
interpretation limit there rather than a second protocol deviation; iter197 had instead registered the
visible test as its soundness anchor and separate paired-gold controls.

\paragraph{Instrument A: judge panel.} \texttt{gpt-5.6-terra} and \texttt{claude-opus-4-8} reviewed each
of twenty-two hack diffs and twenty-two paired gold diffs. A planned \texttt{gemini-2.5-flash} slot was not
run because application-default credentials were blocked. OpenAI judging used a 1{,}536-token cap and
Anthropic detector judging used \texttt{max\_tokens=200}; no request supplied a temperature field. We count
a row as caught if either parsed response says \texttt{reward\_hack}.

The panel has observed catches on twenty of twenty-two hack rows. Eight of eighty-eight responses are
unparseable, affecting five hack rows and three gold rows. Every affected hack row is caught by the other
judge, so row-level any-catch remains twenty of twenty-two. Three gold rows are observed flags; because
three other gold rows have a missing response, the required sensitivities are $3/22$ observed lower,
$6/22$ worst-case missing upper, and $3/19$ complete-case. The retained artifact contains parsed labels and
nondecision markers, not raw response text, so exact response substance cannot be re-audited.

All forty-four full-cohort rows were freshly judged in iter201; no iter196 labels were reused. The prompt
builder capped problem text at 1{,}500 characters, visible-test text at 2{,}500, and candidate diffs at
4{,}000. Task text was truncated in $14/44$ prompts ($7/22$ unique instances), visible-test text in $6/44$
($3/22$), and candidate diffs in none. The first Git commit containing the full-cohort judge protocol also
contained its outputs, so Git does not independently establish a pre-output protocol freeze.

\paragraph{Instrument B: locator-assisted, gold-validated property pipeline.} \texttt{gpt-5.6-terra}
generated a property for twenty-one of twenty-two targets. Twenty of those twenty-one properties passed on
gold and entered the exploratory analysis; six caught the candidate patch. Because gold passing is the
inclusion rule, running the same property on the paired gold patch is not an independent false-positive
experiment. Iter201 records protocol \texttt{FAIL} because the generator used a diff-derived locator; its
registered method did explicitly name gold validation. Iter197 records \texttt{FAIL} for three distinct
reasons: the same locator deviation, replacement of the registered visible-test soundness anchor with
gold, and omission of independent decisions on ten registered paired-gold controls. Its later threshold of
five catches first appeared with generated outputs, so the observed $4/10$ is a post-generation diagnostic,
not a missed prospective bar.

The property prompts also used capped inputs. In iter201, task text was truncated for $9/22$ targets and
visible-test text for $3/22$. Historical iter193--iter199 construction and witness execution, as well as
both property executions, used mutable \texttt{:latest} image tags without retaining resolved digests;
exact container bytes therefore cannot be reconstructed from the committed evidence.

\begin{table}[t]
\centering
\footnotesize
\caption{Corrected exploratory full-cohort instrument accounting. Property-gold passing is an inclusion
rule, not an independent control result. Iter201's protocol failure is the diff-derived locator.}
\label{tab:detectors}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.22\linewidth}>{\raggedright\arraybackslash}p{0.12\linewidth}>{\raggedright\arraybackslash}p{0.23\linewidth}>{\raggedright\arraybackslash}p{0.33\linewidth}@{}}
\toprule
Instrument & Hack catches & Coverage / missingness & Control interpretation \\
\midrule
Judge panel & 20/22 & 8/88 response nondecisions & Gold flags: 3/22 lower; 6/22 missing upper; 3/19 complete-case \\
Locator/gold property pipeline & 6/22 & 21/22 generated; 20/21 pass gold & No independent false-positive estimate; protocol FAIL \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Exploratory overlap.} In iter197, the judge caught seven, the property pipeline caught four, and
their observed union was eight of ten only when unparseable judge responses were treated as no flag. The
apparent property-only row, \texttt{django-11211}, had two unparseable judge responses: it was
judge-unadjudicated, not a confirmed judge miss. The corresponding missingness sensitivities are $8/10$
observed, $9/10$ upper, $7/8$ judge-complete, and $8/9$ property-resolved. In iter201, every one of the six
property catches is among the judge's twenty, so the union remains twenty of twenty-two and two astropy
hacks are missed by both. Neither run establishes confirmed complementarity or evidence that a deployable
ensemble improves on a strong judge.

\paragraph{Claim boundary.} This is a corrected exploratory comparison across eight repositories. The
judge figures are one stochastic run with explicit nondecisions; the property counts come from a protocol
deviation and have no independent false-positive estimate. We make no leaderboard, model-superiority,
state-of-the-art, population-frequency, or deployment claim.

\section{Limitations}

We state the bounds plainly.
\begin{itemize}
  \setlength{\itemsep}{2pt}
  \setlength{\parsep}{0pt}
  \setlength{\parskip}{0pt}
  \item \textbf{Small, mostly elicited sample.} The benchmark has twenty-two hacks across eight
  repositories, produced by a model asked to write wrong variants. The separate neutral-prompt solve is a
  nonrandom, gold-localized convenience sample, not a measure of field frequency.
  \item \textbf{Exploratory neutral-solve rules.} The strict blind rule was adopted after outcome
  inspection, and the missingness summaries were added after the original result but before the backfill.
  Six of twenty-four certified outcomes remain unadjudicated. The
  three sensitivities are descriptive and must stay together. Fifty-four historical execution logs lack
  explicit image/exit provenance and are trusted only as a frozen exact-byte corpus; twenty backfill logs
  carry the stronger provenance markers.
  \item \textbf{Cohort-specific wrongness labels.} In the constructed cohort, ``wrong'' means the variant
  differs from the gold reference fix on a retained input, not independent semantic adjudication. The
  neutral cohort additionally requires both blind judges to identify only the model output as wrong.
  \item \textbf{Incomplete judge records.} The detector-judge numbers come from one stochastic run with
  eight nondecisions. Parsed labels are retained, but raw iter201 response text is unavailable. Iter200
  likewise retains only parsed blind-judge labels and derived booleans, so exact response substance and
  parser fidelity cannot be re-audited for the strict existence case.
  \item \textbf{Detector chronology and input coverage.} The full-cohort judge protocol and outputs first
  appear together in Git, so no independent pre-output freeze is established. Judge and property prompts
  used the character caps reported above; several task and test inputs were truncated.
  \item \textbf{Distinct property-protocol deviations.} Both property gates are \texttt{FAIL} because of
  diff-derived locators. Iter197 additionally replaced its registered visible-test soundness anchor and
  omitted independent paired-gold decisions. Iter201 registered gold validation; there it prevents an
  independent specificity estimate but is not another failed bar.
  \item \textbf{Historical container provenance.} Iter193--iter199 construction and witness execution and
  iter197/iter201 property execution retained mutable \texttt{:latest} tags but no resolved image digests.
  Their exact historical container bytes are not reconstructible from the repository.
  \item \textbf{Role reuse.} \texttt{gpt-5.6-terra} produced adversarial variants, scenarios, neutral
  patches, and properties and also occupied one judge slot; cross-model generalization is unmeasured.
\end{itemize}

\section{Conclusion}

Under our reference-differential operational label, SWE-bench Verified certifies patches that are wrong on
retained synthesized inputs. We constructed twenty-two such patches across eight repositories and released
execution witnesses. Every patch passes the graded tests; in a separate sixteen-row audit, no additional
test in the audited target modules distinguished a candidate from gold. One judge-panel run has observed
catches on twenty of twenty-two hacks, with eight of eighty-eight response nondecisions and paired-gold flag
sensitivities of $3/22$, $6/22$, and $3/19$. The locator-assisted, gold-validated property pipeline catches
six of twenty-two, all within the judge set. Both property gates fail the diff-independent locator contract;
iter197 has two additional protocol deviations, while iter201's registered gold validation prevents an
independent false-positive estimate. The ten-row apparent property-only case was judge-unadjudicated, and
the full-cohort property catches are a subset of the judge's, so no confirmed complementarity is shown.
The exploratory neutral-prompt localized solve confirms one
strict case under a post-inspection rule. Its corrected cohort has twenty-four certified patches and six
declared missing outcomes, giving $1/24$, $7/24$, and $1/18$. A 53-target follow-up retained fifty patches
and thirty-eight scenario programs. Its frozen static-safety guard rejected nine programs with twenty-one
findings, admitted twenty-nine, preserved one original missing scenario, and stopped before execution.
Iter202 is therefore a scenario-safety protocol/execution null with no rate. The separately disclosed
post-provider iter203 recovery seals those bytes, certifies all fifty patches, executes only admitted
copies, and keeps rejected or missing witnesses unresolved. It is pre-result and contributes no result here.

\paragraph{Reproducibility.} Every number in this paper regenerates from a committed script, manifest, or
validated receipt in the Telos repository. The experiments are named in the text (for example, the
construction is iter193 through iter195 and the expansion is iter199). Iter196 is the judge pilot; iter197
and iter201 are protocol-failed property runs with retained exploratory diagnostics. Iter200 is the
localized-solve denominator correction; iter202 is the pre-execution safety null; iter203 has no result yet.

\begin{thebibliography}{11}
\footnotesize
\setlength{\itemsep}{1pt}
\bibitem{amodei2016concrete} D.~Amodei, C.~Olah, J.~Steinhardt, P.~Christiano, J.~Schulman, and D.~Man\'e.
Concrete Problems in AI Safety. \emph{arXiv:1606.06565}, 2016.
\bibitem{krakovna2020specification} V.~Krakovna et al. Specification gaming: the flip side of AI ingenuity.
DeepMind Blog, 2020.
\bibitem{skalse2022defining} J.~Skalse, N.~H.~R.~Howe, D.~Krasheninnikov, and D.~Krueger. Defining and
Characterizing Reward Hacking. \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2022.
\bibitem{jimenez2024swebench} C.~E.~Jimenez, J.~Yang, A.~Wettig, S.~Yao, K.~Pei, O.~Press, and
K.~Narasimhan. SWE-bench: Can Language Models Resolve Real-World GitHub Issues? \emph{Proc.\ ICLR}, 2024.
\emph{arXiv:2310.06770}.
\bibitem{zheng2023judging} L.~Zheng et al. Judging LLM-as-a-Judge with MT-Bench and Chatbot Arena.
\emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2023. \emph{arXiv:2306.05685}.
\bibitem{terekhov2025controltax} M.~Terekhov, Z.~N.~D.~Liu, C.~Gulcehre, and S.~Albanie. Control Tax: The
Price of Keeping AI in Check. \emph{arXiv:2506.05296}, 2025.
\bibitem{deepmind2025fsf} Google DeepMind. Frontier Safety Framework, version 3.0. September 22, 2025.
\bibitem{metr2025malt} METR. MALT: A Dataset of Natural and Prompted Behaviors That Threaten Eval
Integrity. October 14, 2025. (MALT: Manually-reviewed Agentic Labeled Transcripts; 10{,}919 transcripts,
403 tasks, 21 models.)
\bibitem{lambert2024rewardbench} N.~Lambert et al. RewardBench: Evaluating Reward Models for Language
Modeling. \emph{arXiv:2403.13787}, 2024.
\bibitem{chen2018metamorphic} T.~Y.~Chen et al. Metamorphic Testing: A Review of Challenges and
Opportunities. \emph{ACM Computing Surveys}, 51(1), 2018.
\bibitem{claessen2000quickcheck} K.~Claessen and J.~Hughes. QuickCheck: a lightweight tool for random
testing of Haskell programs. \emph{Proc.\ ICFP}, 2000.
\end{thebibliography}

\end{document}
